---
title: "Draft"
output:
  html_document:
    df_print: paged
---

In this workshop we will use the following packages:

-   `rnaturalearth` - provides access for the [Natural Earth](http://www.naturalearthdata.com/). The Natural Earth is a public domain map dataset including vector country and other administrative boundaries

-   `sf` for setting the map object class and plot it

-   `mapview`, `tmap`, and `ggplot2` for plotting the map objects

-   `coronavirus`, `covid19italy` to pull Covid19 data at different levels (e.g., region, country, etc.)

```{r}
library(sf)
library(rnaturalearth)
library(mapview)
library(tmap)
library(ggplot2)
library(dplyr)
library(tidyr)
library(rvest)
library(coronavirus)
```

### Polygons

```{r}
plot(x = 1, 
     y = 1,
     ylab = "",
     xlab = "",
     main = "Point")

```

```{r}

plot(x = c(1, 2, 3), y = c(1, 4, 2), type = "l")

```

```{r}
plot(x = c(1, 2, 4, 3, 1), y = c(1, 4, 3, 1, 1), type = "l")
```

labels + polygons = map boarders

labels + polygons + data = choropleth map

```{r}
world <- ne_countries(type = 'countries', scale = 'small', returnclass = "sf")
str(world)
head(world)
plot(world$geometry)
```

```{r}

africa <- world %>% filter(continent == "Africa")
plot(africa$geometry)
```

```{r}
w_africa <- world %>% filter(subregion == "Western Africa")
plot(w_africa$geometry, col = sf.colors(12, categorical = TRUE), border = 'grey', 
     axes = TRUE, main = "Western Africa")
```

```{r}
nigeria <- ne_states(country = "Nigeria", returnclass = "sf")

head(nigeria)
plot(nigeria$geometry, col = sf.colors(37, categorical = TRUE), border = 'grey', 
     axes = TRUE, main = "Nigeria")
```

```{r}
  
url <- "https://en.wikipedia.org/wiki/List_of_Nigerian_states_by_population"

page <- read_html(url)
tables <- html_node(page, ".wikitable")
pop_table <- html_table(tables, fill = TRUE) %>%
  select(state_temp = State, pop_2006_temp = `Population (2006)`, pop_2016_temp = `Population (2016)`)


pop_table$pop_2006 <- as.numeric(gsub(x = pop_table$pop_2006_temp,pattern = ",", replacement = ""))
pop_table$pop_2016 <- as.numeric(gsub(x = pop_table$pop_2016_temp,pattern = ",", replacement = ""))
pop_table$state <- gsub(x = pop_table$state_temp,pattern = " State", replacement = "")
pop_table <- pop_table %>% select(-state_temp, -pop_2006_temp, - pop_2016_temp) %>%
  select(state, pop_2006, pop_2016) %>%
  mutate(state_fix = state)

pop_table$state_fix[which(pop_table$state_fix == "Nasarawa")] <- "Nassarawa"

head(pop_table)
```

```{r}
nigeria_pop <- nigeria %>% left_join(pop_table, by = c("name" = "state_fix"))

plot(nigeria_pop["pop_2016"], key.pos = 1, axes = TRUE, key.width = lcm(1.3), key.length = 1.0)


tm_shape(nigeria_pop) +
    tm_polygons(col = "pop_2016", 
                style = "order",
                title = "Population",
                palette = "Blues") +
   tm_style("cobalt") + 
   tm_text("state", size = 0.7) +
  tm_credits("Source: Wikipedia - List of Nigerian states by population",
             position = c("LEFT", "BOTTOM")) + 
  tm_layout(title= "Nigeria Population by States", 
            title.position = c('right', 'top') ,
            inner.margins = c(0.02, .02, .1, .15))
```

### Data

```{r}
covid19_daily <- refresh_coronavirus_jhu()

head(covid19_daily)

df <- covid19_daily %>%
  filter(location_type == "country") %>%
  group_by(location, data_type) %>%
  summarise(cases = sum(value),
            .groups = "drop") %>%
  pivot_wider(names_from = data_type, values_from = cases) %>%
  setNames(c("country", "total_cases", "total_death"))
  
  

head(df)

df1 <- covid19_daily %>%
  filter(location_type == "country") %>%
  group_by(location, location_code, data_type) %>%
  summarise(cases = sum(value),
            .groups = "drop") %>%
  pivot_wider(names_from = data_type, values_from = cases) %>%
  setNames(c("country", "total_cases", "total_death"))



world_covid <- world %>% 
  select(country = sovereignt, geometry) %>%
  left_join(df, by = "country")


plot(world_covid)
plot(world_covid[, c("total_cases")])
```

### 

### Data Visualization

```{r}
world <- ne_countries(type = 'countries', scale = 'large')
sp::plot(world)

world <- ne_countries(type = 'countries', scale = 'small', returnclass = "sf")
world$random <- stats::rnorm(n = nrow(world))
sf::plot_sf(world)
sp::plot(world[, "random"])
sp::plot(world[which(world$region_un == "Africa"), "random"])

x1 <- rnaturalearth::ne_countries(country = 'Nigeria', type='countries')
sp::plot(x1)

# x2 <- rnaturalearth::ne_states(country = 'Nigeria')

```

```{r}

mapview::mapview(x)

# tmap::
```
